---
title: "Exponential Distribution Simulation"
author: "Mark Culp"
date: "March 25, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview:
This paper explores simulations on an Exponential Distribution.  

```{r}

# Set parameters for distribution
n <- 40 
lambda <- 0.2




# An exploratory plot 

```

## Simulations:  

```{r}
set.seed(0)

# Generate 1,000 random deviates for an exponential distribution
sampleExpDist <- rexp(1000, lambda)

# Generate a distribution of 1000 averages of 40 
# random deviates for an exponential distribution
# and calculate the variances in each sample
expSample = NULL
mnsExpDist = NULL
varExpDist = NULL
for (i in 1 : 1000) {
  expSample = rexp(n, lambda)
  mnsExpDist = c(mnsExpDist, mean(expSample))
  varExpDist = c(varExpDist, var(expSample))
}

# Create a histogram of the distribution of exponentials
hist(sampleExpDist)

# Create histogram of the distribution of exponential averages
hist(mnsExpDist)

```

## Sample Mean versus Theoretical Mean
This distribution is centered at ...  The theoretical center, or mean of the distribution is centered at ...

```{r}

# Load libraries
library(knitr)

# Calculate the mean of the sample exponential distribution
sampleExpDistMean <- round(mean(sampleExpDist),3)

# Calculate mean of the distribution of exponential averages
mnsDistMean <- round(mean(mnsExpDist),3)

# Calculate hypothetical mean for the exponential distribution
hypoDistMean <- 1/lambda

# Combine means in a row
rowMeans <- rbind(c(sampleExpDistMean, mnsDistMean, hypoDistMean))

# Display table of calculated means
kable(rowMeans, caption = "Comparison of Sample and Hypothetical Means", col.names = c("Sample","Averages","Hypothetical"), align = 'c')

```

## Sample Variance versus Theoretical Variance
This distribution's variance is ... The theoretical  variance of this distribution would be ...

```{r}

# Calculate variance of the sample exponential distribution
sampleExpDistVariance <- round(var(sampleExpDist),3)

# Calculate variance of the distribution of exponential averages
mnsExpDistVariance <- round(mean(varExpDist),3)

# Calculate hypothetical mean for the exponential distribution
hypoDistVariance <- (1/lambda)^2

# Combine variances in a row
rowVar <- rbind(c(sampleExpDistVariance, mnsExpDistVariance, hypoDistVariance))

# Display table of calculated variances
kable(rowVar, caption = "Comparison of Sample and Hypothetical Variances", col.names = c("Sample","Averages","Hypothetical"), align = 'c')

```

## Distribution
We know this distribution is normal because ...



Our conclusions and assumptions ... 

```{r}


```



