---
title: "Simulation Exercise"
author: "Mark Culp"
date: "March 25, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview:
This paper explores simulations on an Exponential Distribution.  

```{r}

# Set parameters for distribution
n <- 40 
lambda <- 0.2

set.seed(0)

# Generate random deviates for a sample exponential distribution
sampleDist <- rexp(n, lambda)


# An exploratory plot 

```

## Simulations:  

```{r}
```

## Sample Mean versus Theoretical Mean
This distribution is centered at ...  The theoretical center, or mean of the distribution is centered at ...

```{r}

# Calculate mean of the sample distribution
sampleDistMean <- mean(sampleDist)

# Calculate hypothetical mean for the exponential distribution
hypoDistMean <- 1/lambda

```

## Sample Variance versus Theoretical Variance
This distribution's variance is ... The theoretical  variance of this distribution would be ...

```{r}

# Calculate variance of the sample distribution
sampleDistVariance <- var(sampleDist)

# Calculate hypothetical variance for the exponential distribution
hypoDistVariance <- (1/lambda)^2


```

## Distribution
We know this distribuion is normal because ...



Our conclusions and assumptions ... 

```{r}

hist(runif(1000))

#---

mns = NULL
for (i in 1:1000) mns = c(mns, mean(runif(40)))
hist(mns)


```



